### 2018-11-13 Sections/essays_quantum_ecosystem.tex
minor

\begin{itemize}
\item Quantum operations: vendors selling the capacity for non-trivial state preparation (e.g NOON\index{NOON states} and states GHZ\index{GHZ states}), or measurements (e.g complex syndrome measurements).

@@

\item Classical control:\index{Classical control} Many quantum protocols require intermediate classical control. For example, in a quantum repeater network we must control the order of entangling operations and track local Pauli corrections accumulated by the final entangled Bell-pair.

>>>>

\begin{itemize}
\item Quantum operations: vendors selling the capacity for non-trivial state preparation (e.g NOON\index{NOON states} and states GHZ\index{GHZ states}), or measurements (e.g complex entangling syndrome measurements\index{Syndrome measurements}).

@@

\item Classical control:\index{Classical control} Many quantum protocols require intermediate classical control, for example for feedforward\index{Feedforward}. For example, in a quantum repeater network we must control the order of entangling operations and track local Pauli corrections accumulated by the final entangled Bell-pair.
